### 2020-02-12 README.Rmd
Fix some spelling typos

The `county_rain` function takes a list of county FIPS codes, bounds on the starting and ending years of the analysis, and thresholds to define rain-based exposure (cumulative rainfall and distance from the storm's track, as explained for the binary rain maps shown in an earlier section) and creates a list of all storms that met these thesholds for the counties. For example, to get a dataset of all the storms to which Orleans Parish (FIPS 22071), and Newport News, Virginia (FIPS 51700), were exposed between 1995 and 2005, where "exposed" means that the storm passed within 100 kilometers of the county center and the rainfall over a three-day window of the date of closest approach was 100 millimeters or more, you can run:

>>>>

The `county_rain` function takes a list of county FIPS codes, bounds on the starting and ending years of the analysis, and thresholds to define rain-based exposure (cumulative rainfall and distance from the storm's track, as explained for the binary rain maps shown in an earlier section) and creates a list of all storms that met these thresholds for the counties. For example, to get a dataset of all the storms to which Orleans Parish (FIPS 22071), and Newport News, Virginia (FIPS 51700), were exposed between 1995 and 2005, where "exposed" means that the storm passed within 100 kilometers of the county center and the rainfall over a three-day window of the date of closest approach was 100 millimeters or more, you can run:
